City-GAN: Learning architectural styles using a custom Conditional GAN architecture

### 2019-07-02 paper.tex
Add nvidia acknowledgement

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
Generative Adversarial Networks (GANs) are a well-known technique that is trained on samples (e.g.~pictures of fruits) and which after training is able to generate realistic new samples. Conditional GANs (CGANs) additionally provide label information for subclasses (e.g.~apple, orange, pear) which enables the GAN to learn more easily and increase the quality of its output samples. We use GANs to learn architectural features of major cities and to generate images of buildings which do not exist. We show that currently available GAN and CGAN architectures are unsuited for this task and propose a custom architecture. We show that our architecture has superior performance for this task and verify its capabilities with extensive experiments. 
\end{abstract}

@@

After achieving suboptimal results with this CGAN architecture we tried a different approach and modified the discriminator: instead of adding the one-hot-encoded vector with the city information after the convolution, we decided to add it as an input to each pixel in the beginning of the convolution. Thus, additional to the RGB values, each pixel also has the one-hot-encoded information of the city. For example, with four cities, each pixel has 7 color channels: 3 for the colors and 4 for the one-hot-encoded cities.

@@

\begin{figure}
\includegraphics[width=\columnwidth]{figures/architectures/maxnet.pdf}
\caption{The architecture of our neural network is inspired by \cite{pytorch_deep_2019}. The difference in our custom architecture is that labels are fed into the generator as well as into the discriminator alongside the data.}  % TODO
\label{fig:maxnet}
\end{figure}

@@

>>>>

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
Generative Adversarial Networks (GANs) are a well-known technique that is trained on samples (e.g.~pictures of fruits) and which after training is able to generate realistic new samples. Conditional GANs (CGANs) additionally provide label information for subclasses (e.g.~apple, orange, pear) which enables the GAN to learn more easily and increase the quality of its output samples. We use GANs to learn architectural features of major cities and to generate images of buildings which do not exist. We show that currently available GAN and CGAN architectures are unsuited for this task and propose a custom architecture and demonstrate that our architecture has superior performance for this task and verify its capabilities with extensive experiments. 
\end{abstract}

@@

After achieving suboptimal results with this CGAN architecture we tried a different approach and modified the discriminator: instead of adding the one-hot-encoded vector with the city information after the convolution, we decided to add it as an input to each pixel in the beginning of the convolution. Thus, additional to the RGB values, each pixel also has the one-hot-encoded information of the city. For example, with four cities, each pixel has 7 color channels: 3 for the colors and 4 for the one-hot-encoded cities (\autoref{fig:maxnet}).

\begin{figure}
\includegraphics[width=\columnwidth]{figures/architectures/maxnet.pdf}
\caption{The architecture of our neural network is inspired by \cite{pytorch_deep_2019}. The difference in our custom architecture is that labels are fed into the generator (top) as well as into the discriminator (bottom) alongside the data.}  % TODO
\label{fig:maxnet}
\end{figure}

@@

@@

\section*{Acknowledgement}
% We thank NVIDIA Corporation for donating a Titan Xp.
% The Titan Xp we used was donated by NVIDIA.
The Titan Xp used for this research was donated by the NVIDIA Corporation.
